### 2021-04-08 Chapter-5/Chapter-5.tex
Updates from Overleaf

The method has three phases. In the first phase, we fuzz the target program with various inputs and collect the memory access information. In the second phase, we map the memory access information with the source code. With the debug information, we can precisely know the address access information of the source code. In the third phase, we exam the source code, if one function have two memory access patterns, then the function is vulnerable to side-channel attacks. Base on the distribution of memory access patterns under different inputs, we quantify the side-channel leakage of each functions.

>>>>

The method consists of three phases. In the first phase, we fuzz the target program with various inputs and collect the memory access information. In the second phase, we map the memory access information with the source code. With the debug information, we can precisely know the address access information of the source code. In the third phase, we exam the source code. If one function has two memory access patterns, then the function is vulnerable to side-channel attacks. Based on the distribution of memory access patterns under different inputs, we quantify each function's side-channel leakage.
